Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-01-17 awipev-CO2.Rmd
some script updates in discrete ATCT part

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

# Add the flag location: some samples have been collected at the peer. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00", 1,0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

>>>>

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

# Add the flag location: some samples have been collected at the peer. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)
